WASP-4 is Accelerating Towards the Earth

### 2020-01-29 paper/ms.tex
minor

Figure~\ref{fig:times} shows the observed transit times, minus the
best-fit constant period model.  The best-fitting constant-period
model has 91 degrees of freedom, $\chi^2 = 276$,  and $\chi^2_{\rm
red}=3.0$.  The best-fitting quadratic model has 90 degrees of freedom,
$\chi^2 = 183$, and $\chi^2_{\rm red}=2.0$.  The difference in the
Bayesian information criteria (BIC) between the linear and quadratic
and models is $\Delta {\rm BIC} = 89.1$, strongly favoring the
quadratic case \citep{kass_bayes_1995}.

@@

Our initial model for the radial velocity data was a single Keplerian
orbit, plus instrument offsets, jitters, and a long-term trend
\citep[][\texttt{radvel}]{fulton_radvel_2018}.  We set Gaussian priors
on the orbital period and time of inferior conjunction using the
values from Table~4 of \citetalias{bouma_wasp4b_2019}, and fixed
WASP-4b's eccentricity to zero
\citep{beerer_secondary_2011,knutson_friends_2014,bonomo_gaps_2017}.
The free parameters were the velocity semi-amplitude, the instrument
zero-points, an additive ``white noise'' instrument jitter for each
instrument, linear ($\dot{v_{\rm r}}$), and optionally second-order
($\ddot{v_{\rm r}}$) acceleration terms.

%FIXME: this is a janky approach if so??
We found that the best-fitting model with both linear and quadratic
radial velocity terms was marginally preferred (by $\Delta
\mathrm{BIC} = 5.8$) over the best-fitting model with only a linear
term.  Regardless, for consistency with \citet{knutson_friends_2014},
who fixed the quadratic component of the long-term trend to zero, in
Figure~\ref{fig:rvs} we show best-fitting models for the linear-trend
case.

WASP-4 was found to be accelerating towards our line-of-sight at high
confidence,
\begin{equation}
  \dot{v}_{\rm r} = \dot{\gamma} = 
     -0.0422^{+0.0028}_{-0.0027}
     \,{\rm m}\,{\rm s}^{-1}\,{\rm day}^{-1}.
\end{equation}
For comparison, before our new measurements, $\dot{v}_{\rm r}$ was
thought to be about five times smaller, and was only marginally
significant \citep{knutson_friends_2014,bouma_wasp4b_2019}.

>>>>

Figure~\ref{fig:times} shows the observed transit times, minus the
best-fit constant period model.  The best-fitting constant-period
model has 91 degrees of freedom, $\chi^2 = 276$,  and $\chi^2_{\rm
red}=3.0$.  The best-fitting quadratic model has 90 degrees of freedom,
$\chi^2 = 183$, and $\chi^2_{\rm red}=2.0$.  The difference in the
Bayesian information criteria (BIC) between the linear and quadratic
and models is $\Delta {\rm BIC} = 89$, strongly favoring the
quadratic case \citep{kass_bayes_1995}.

@@

Our initial model for the radial velocity data was a single Keplerian
orbit, plus instrument offsets, jitters, and a long-term linear trend
\citep[][\texttt{radvel}]{fulton_radvel_2018}.  We set Gaussian priors
on the orbital period and time of inferior conjunction using the
values from Table~4 of \citetalias{bouma_wasp4b_2019}, and fixed
WASP-4b's eccentricity to zero
\citep{beerer_secondary_2011,knutson_friends_2014,bonomo_gaps_2017}.
The free parameters were the velocity semi-amplitude, the instrument
zero-points, an additive ``white noise'' instrument jitter for each
instrument, and a linear ($\dot{v_{\rm r}}$) acceleration term.  We
also considered a model without the linear trend, and found that it
was disfavored by $\Delta {\rm BIC}=73$.

In the preferred ``planet+trend'' model, WASP-4 is accelerating
towards our line-of-sight at high confidence,
\begin{equation}
  \dot{v}_{\rm r} = \dot{\gamma} = 
     -0.0422^{+0.0028}_{-0.0027}
     \,{\rm m}\,{\rm s}^{-1}\,{\rm day}^{-1}.
\end{equation}
For comparison, before our new measurements, $\dot{\gamma}$ was
thought to be about five times smaller, and had marginal statistical significance
\citep{knutson_friends_2014,bouma_wasp4b_2019}.
